\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-03-24 k-planar.tex
Numbers to bullets , got rid of final section

@@

Combining \cref{non-repetitive} with our results on product structure, we obtain the following corollary:
\begin{cor}\label{nonrepetitive_cor}
  The following bounds hold for the nonrepetitive chromatic number of any graph from each of the following classes:
  \begin{compactenum}
    \item $k$-planar: $(18k^2+48k+30)\cdot 4^{\binom{k+4}{3}}$
    \item $(g,k)$-planar: $\max\{2g,3\}\cdot(6k^2+16k+10) 4^{\binom{k+4}{3}}$
    % \item $(g,\delta)$-string: $g4^{O(\delta^3)}$
    \item $1$-planar: $1792$
    \item $d$-map: $256(d+3\floor{d/2}-3)$
    % \item $(g,d)$-map: $g4^{O(d)}$
    % \item $k$-NN: $4^{O(k^6)}$
    \item $(g,d)$-map graph: $(7d^2-21d)\cdot 4^{10}$
  \end{compactenum}
\note{DW}{I prefer bullets here}
\end{cor}

@@

\begin{cor}\label{p_centered_cor}
  The following bounds hold for the $p$-centered chromatic number of any graph from each of the following classes:
  \begin{compactenum}
    \item $k$-planar: $(18k^2+48k+30)\cdot 4^{\binom{k+4}{3}}$
    \item $(g,k)$-planar: $\max\{2g,3\}\cdot(6k^2+16k+10)(p+1)\binom{p+\binom{k+4}{3}-1}{\binom{k+4}{3}-1}$
    % \item $(g,\delta)$-string: $g4^{O(\delta^3)}$
    \item $1$-planar: $7(p+1)^2(p\ceil{\log(p+1)}+2p+1)$
    \item $d$-map: $(d+3\floor{d/2}-3)\cdot (p+1)^2(p\ceil{\log(p+1)}+2p+1)$
    % \item $(g,d)$-map: $g4^{O(d)}$
    % \item $k$-NN: $4^{O(k^6)}$
    \item $(g,d)$-map: $\max\{2g,3\}\cdot 7d(d-3)(p+1)\cdot \binom{p+9}{9}$
  \end{compactenum}
\note{DW}{I prefer bullets here}
\end{cor}

@@

\section{Wrapping Up}
\label{WrappingUp}

\note{DW}{This problem does not deserve a section of its own. Move to end of \cref{gk_planar_section}?}

We finish with an open problem. \cref{kPlanarProduct} shows that every $k$-planar graph is contained in $H\boxtimes P \boxtimes K_\ell$ for some graph $H$ with treewidth $O(k^3)$ where $\ell\leq O(k^2)$. Does there exist a function $\ell:\N\to\N$ and a universal constant $C$ such that every $k$-planar graph is contained in $H\boxtimes P \boxtimes K_{\ell(k)}$ for some graph $H$ with treewidth at most $C$?  Perhaps $C=3$. Note that $C\geq 3$ even for planar graphs \citep{DJMMUW20}.

>>>>

\cref{kPlanarProduct} shows that every $k$-planar graph is contained in $H\boxtimes P \boxtimes K_\ell$ for some graph $H$ with treewidth $O(k^3)$ where $\ell\leq O(k^2)$.  In some applications, the treewidth of $H$ is much more important than the value of $\ell$, which leads to the following question:

\noindent\textbf{Open Problem:}
  Does there exist a function $\ell:\N\to\N$ and a universal constant $C$ such that every $k$-planar graph is contained in $H\boxtimes P \boxtimes K_{\ell(k)}$ for some graph $H$ with treewidth at most $C$?  Perhaps $C=3$, which is the case for planar graphs (\cref{PlanarProduct}(b)) and for $1$-planar graphs (\cref{1_planar_product}). Note that $C\geq 3$ even for planar graphs \citep{DJMMUW20}.

@@

Combining \cref{non-repetitive} with our results on product structure, we obtain the following corollary:
\begin{cor}\label{nonrepetitive_cor}
  The following bounds hold for the nonrepetitive chromatic number of any graph from each of the following classes:
  \begin{compactitem}
    \item $k$-planar: $(18k^2+48k+30)\cdot 4^{\binom{k+4}{3}}$
    \item $(g,k)$-planar: $\max\{2g,3\}\cdot(6k^2+16k+10) 4^{\binom{k+4}{3}}$
    % \item $(g,\delta)$-string: $g4^{O(\delta^3)}$
    \item $1$-planar: $1792$
    \item $d$-map: $256(d+3\floor{d/2}-3)$
    % \item $(g,d)$-map: $g4^{O(d)}$
    % \item $k$-NN: $4^{O(k^6)}$
    \item $(g,d)$-map graph: $(7d^2-21d)\cdot 4^{10}$
  \end{compactitem}
\end{cor}

@@

\begin{cor}\label{p_centered_cor}
  The following bounds hold for the $p$-centered chromatic number of any graph from each of the following classes:
  \begin{compactitem}
    \item $k$-planar: $(18k^2+48k+30)\cdot 4^{\binom{k+4}{3}}$
    \item $(g,k)$-planar: $\max\{2g,3\}\cdot(6k^2+16k+10)(p+1)\binom{p+\binom{k+4}{3}-1}{\binom{k+4}{3}-1}$
    % \item $(g,\delta)$-string: $g4^{O(\delta^3)}$
    \item $1$-planar: $7(p+1)^2(p\ceil{\log(p+1)}+2p+1)$
    \item $d$-map: $(d+3\floor{d/2}-3)\cdot (p+1)^2(p\ceil{\log(p+1)}+2p+1)$
    % \item $(g,d)$-map: $g4^{O(d)}$
    % \item $k$-NN: $4^{O(k^6)}$
    \item $(g,d)$-map: $\max\{2g,3\}\cdot 7d(d-3)(p+1)\cdot \binom{p+9}{9}$
  \end{compactitem}
\end{cor}

@@
